First and foremost, I would like to express my sincere gratitude
Prof. Natacha CHETCUTI-OSOROVITZ,
Prof. Salah EL AYOUBI,
Prof. TRAN Trong Hieu
for their invaluable guidance and mentorship throughout the course of this thesis.

I also would like to sincerely thank
Prof. Arnaud BOURNEL in Université Paris-Saclay,
Prof. Pierre DUHAMEL in CentraleSupélec - Université Paris-Saclay,
Prof. NGUYEN Linh Trung and Dr. NGUYEN Hong Thinh in VNU - University of Engineering and Technology.
Their assistance during the joint master’s program and the internship in France was instrumental.

I am fortunate to have been a member of the UMICROWD project.
This is a memorable time for me to work in a very professional environment in France, with beloved teachers and friends who always support me in my research work as well as in social life.

I extend my gratitude to my employer, VIETTEL cooperation, for providing me with the opportunity to study abroad and for their support during my time in France.

I reserve my deepest and heartfelt thanks go to my family,
whose immense support and encouragement have been a constant source of strength.
I am also thankful to my friends who have helped me navigate the challenges of studying abroad,
and to my girlfriend for her diligent review of my writing.

As I worked on this Master Thesis, I encountered several challenges due to my limited experience and time constraints. I am hopeful for the understanding and constructive feedback from the lecturers in the Council, which will enhance my understanding and perspective of the thesis.

\begin{flushright}
	\textit{Chilly-Mazarin, December 10th 2023}

	Student
	\textit{Tien-Dat NGUYEN}
\end{flushright}